Transforming Partially Ordered HTN Problems to Totally Ordered

### 2022-11-08 paper/paper-mainfile.tex
fix Alg labelling, Complex Linearization called Complex Inference now

For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type. For a grounded model, $f' = f$. The inferred preconditions and effects for a task are then defined as below:
\begin{align*}
& \forall t \in T_P : \PreS(t) := \Pre(t) \\
& \forall t \in T_P : \AddS(t) := \Add(t) \\
& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
\end{align*}

@@

\begin{algorithm}\label{alg:Algorithm1}
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

@@

\subsection{Theoretical Properties of Linearization Result}
\begin{theorem}\label{thm:Runtime}
	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes at most quadratic time, $\mathcal{O}( |M| * |F| * |T|^2)$. 
\end{theorem}
\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
	Let $|T|$ = $|T_P| + |T_C|$.

@@

\section{Complex Linearization Procedure}

The work by \cite{ConnyPreEff}, details a way to infer a subset of the mandatory preconditions and effects.

We can use these as an alternative input to Algorithm~\ref{alg:Algorithm1}.

@@

As we can see, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
As we can see, the best planner is ? planner.

>>>>

\subsection{Simple Inference}
For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type. For a grounded model, $f' = f$. The inferred preconditions and effects for a task are then defined as below:
\begin{align*}
& \forall t \in T_P : \PreS(t) := \Pre(t) \\
& \forall t \in T_P : \AddS(t) := \Add(t) \\
& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
\end{align*}

\subsection{Complex Inference}
The work by \cite{ConnyPreEff}, details a way to infer a subset of the mandatory preconditions and effects.

There exists a polynomial-time algorithm for inferring the precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.

We can use these as an alternative input to Algorithm~\ref{alg:Algorithm1}. Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.

\subsection{Linearization Using Inferred Preconditions and Effects}

@@

\begin{algorithm}
	\caption{Linearization using inferred set of preconditions and effects}
	\label{alg:Algorithm1}	
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

@@

\section{Theoretical Properties of Linearization Result}

We now discuss the implications of the above-described linearization procedure.

\subsection{Theoretical Properties If Using Simple Inference}
\begin{theorem}\label{thm:Runtime}
	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes at most quadratic time, $\mathcal{O}( |M| * |F| * |T|^2)$. 
\end{theorem}
\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
	Let $|T|$ = $|T_P| + |T_C|$.

@@

\subsection{Theoretical Properties If Using Complex Inference}
Unfortunately, no criteria for determining if a solution is guaranteed to exist when using the second inference method, since there may always be unknown preconditions and effects in the precondition-relaxed effects.

@@

\begin{table}[h]
	\scalebox{0.4} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }    \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			Coverage \\ 
			Norm. coverage  \\ 
			\bottomrule
		\end{tabular} 	
	}
\end{table}

\begin{table}[h]
	\scalebox{0.4} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }  \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			IPC \\
			\bottomrule
		\end{tabular} 	
	}
\end{table}

\newpage
As we can see, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
The planner that has achieved the highest overall coverage and IPC score is ? planner.
